A free/open-source Kazakh-Tatar machine translation system

### 2013-04-17 paper/paper.tex
past tense semantic differences

> Past tense system

>>>>

The past tense systems of Kazakh and Tatar also do not correspond.  At a basic level, Kazakh differentiates [±eyewitness]\footnote{``Eyewitness'' is a convenient term for this feature, though it may equate more to sureness of knowledge.} (where [-eyewitness] is used in cases of newly discovered information) and [±recent] in the past tense, whereas Tatar has only three categories: eyewitness, non-eyewitness, and newly-acquired-information ---all with no [±recent] distinction).  The result of this is a many-to-many correspondence.  For example, Tatar has a single non-eyewitness past tense morpheme (\texttt{-GAн}) while Kazakh has a recent non-eyewitness past (\texttt{-IптI}) and a distant non-eyewitness past (\texttt{-GAн екен-}).  On the other hand, these two non-eyewitness past forms are used for newly acquired information in Kazakh, whereas in Tatar non-eyewitness (\texttt{-GAн-}) and newly-acquired-information (\texttt{-GAн- икән}) past tenses are distinguished.
> Past tense system
